### 2023-11-20 main.tex
^'^'

 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} become simpler. As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly. Finally, reversing the transformations we retrieve $|\Psi\rangle$.
 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 

@@

We observe that 

@@

with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$. Thus we have

@@

Therefore, it follows that 

@@

	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\

@@

	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(y_{k},c_{k},\ldots,c_{m})\co
where in the second line we have used the resolution of the identity, in the last line we have used \eqref{ABS_1} and in the last equality we have used the definition of \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec}.  
Using the binomial theorem we have that 

@@

\subsection{Explicit steady state of $H$}\label{appB}

@@

\begin{proposition}[Non-equilibrium steady state]

@@

			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\dots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})%\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
	and where 
			\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}g_{x}(x,c_{x},\ldots,c_{L})\\&
			\;\;\;\;\;\;\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{c_{q_{k}}}\beta_{i_{q_{k}}}^{1-c_{q_{k}}}\right)\left(\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\right)

@@

		Q(x)=\sum_{k=1}^{b}\delta_{x,q_{k}}
and $f(c_{1},\ldots,c_{L})$ and $g_{x}(x,c_{x},\ldots,c_{L})$ defined in \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies} respectively. 

@@

\end{proposition} 

@@

	In the equilibrium case, when  $\alpha_{a}=\beta_{a}$ for all $a\in\{1,\ldots,N\}$ only the terms with $c_{x}=0$ do survive in \eqref{SteadyState-coeff-implicit}. Therefore we obtain 

@@

@@

	meaning that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,

@@

				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})
		In the second equality we have rewritten the product by introducing the summation over $b$ and introducing the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$. In the last equality we have used equation \eqref{ABS_1}. 

@@

				indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
			Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
			\begin{remark}[Non-equilibrium steady state using exact correlations]
			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
					%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, we have that 
				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
					where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
							\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
							\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
					Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
						\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
					Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
						\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
			\begin{proposition}[Normalization]
				The steady state $|\Psi\rangle$ is normalized, i.e.
					\sum_{\bm{\tau}\in\Omega^{'}}\langle \bm{\tau}|\Psi\rangle=1
			\end{proposition}
			\textbf{Proof}: Considering \eqref{notation-PSI}, we aim to show that 
				\sum_{\bm{\tau}\in \Omega^{'}}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega^{'}}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
			We introduce an index $\ell\in \{0,\ldots,L\}$ that represents the number of empty occupations for an arbitrary $\bm{\tau}$, i.e. $\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$. Moreover, we introduce the space 
				\Omega_{\ell}^{'}=\left\{\bm{\tau}\in \Omega^{'}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
			Therefore, we can rewrite the normalization condition as 
				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})\nonumber
				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
			We first observe that, using \eqref{ABS}, we have that 
				\Psi^{'}(N,\ldots,N)=1\co
			thus, it is enough to prove that
				&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})\nonumber
				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
			We now consider the second term of the above expression. For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}^{'}$ has $\ell<b$, then this term do not produce any contribution. On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}^{'}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$. Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species. By calling $r=\ell-b$ if $b\leq \ell$ we have that 
				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<i_{q_{b}\leq L}=1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
				=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}^{'}}\Psi^{'}(\bm{\tau})\dt
			As a consequence we have that the normalization condition reads
				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})=0\dt
			By exchanging the summations we have 
				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})=0\dt
			It is enough to prove that, for any fixed $\ell\in\{0,\ldots, L-1\}$ we have that 
				1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=0
			This is true because of the binomial theorem, indeed 
				1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=\sum_{b=0}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=(1-1)^{L-\ell}=0
			that implies the normalization of the state $|\Psi\rangle$. 

>>>>

 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} become simpler. As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly. Finally, reversing the transformations we retrieve $|\Psi\rangle$, i.e. the vector whose components are the probabilities of a certain configuration of the process in the non-equilibrium steady state.
 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlation in the non-equilibrium steady state. The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 

@@

We fix $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$ and we have 

@@

Thus it follows that 

@@

Therefore, it follows that, using the resolution of the identity

@@

	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle
Using $\Psi^{'}(\bm{\tau})$ in \eqref{ABS_1} we have 
	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\

@@

	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\co
where in the last equality we have used the definition of \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies}.
As a last step, using the binomial theorem, we rewrite the previous expression as a polynomial in the boundary densities: 

@@

\subsection{Steady state}\label{appB}

@@

\begin{corollary}[Non-equilibrium steady state]

@@

	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{b}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
%	and where 
	%		\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}g_{x}(x,c_{x},\ldots,c_{L})\\&
%			\;\;\;\;\;\;\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{c_{q_{k}}}\beta_{i_{q_{k}}}^{1-c_{q_{k}}}\right)\left(\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\right)

@@

%	with
%		Q(x)=\sum_{k=1}^{b}\delta_{x,q_{k}}
%and $f(c_{1},\ldots,c_{L})$ and $g_{x}(x,c_{x},\ldots,c_{L})$ defined in \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies} respectively. 

@@

\end{corollary} 

@@

	In the equilibrium case, when  $\alpha_{a}=\beta_{a}$ for all $a\in\{1,\ldots,N\}$ we obtain 

@@

	where the notation
	\begin{equation}%\label{notation-PSI}

@@

	means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,

@@

				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
where the notation
		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$. In the last equality we have summed over all possible $\sigma\in \Omega^{'}$. From Section \ref{correlation-section} we recall that the components of $|\Psi^{'}\rangle$ are the correlation in the non-equilibrium steady state. Thus, we have that  
			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{b}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]

@@

				indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
			\end{comment}
			Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
			\begin{flushright}
				$\square$
			\end{flushright}
		\begin{comment}
			\begin{remark}[Non-equilibrium steady state using exact correlations]
			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
				\begin{align}
					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
					%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
				\end{align}
				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, we have that 
				\begin{equation}
				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
				\end{equation}
			where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and can be computed using \eqref{exactCorrelations}. 
				\end{remark}
		\end{comment}
				\begin{comment}
					where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
					\begin{equation}
						\begin{cases}
							\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
							\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
						\end{cases}
					\end{equation}
					Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
					\begin{equation}
						\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
					\end{equation}
					Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
					\begin{equation}
						\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
					\end{equation}
				\end{comment}
